Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations

### 2024-09-19 main.tex
add paragraph on spanning trees

>>>>

For the agenda of this section, the following combinatorial notion of triangulations will be helpful. 
Whenever $\calT$ is a strongly connected $n$-dimensional triangulation, 
a \emph{spanning tree} is an enumeration $T_{0}, \dots, T_{M}$ of all its $n$-dimensional simplices
where for each index $1 \leq m \leq M$ we have fixed index $0 \leq j(m) \leq m-1$ 
such that $T_{m}$ and $T_{j(m)}$ share a common face of dimension $n-1$.
We call $T_{j(m)}$ the \emph{predecessor} of $T_{m}$ within the spanning tree.
